A systematic search for transiting planets using \KT

### 2015-02-12 ms.tex
words about vetting

\paragraph{Machine vetting}

To generate an initial candidate list, we start by .

@@

There are many instrumental or astrophysical effects that can mimic a transit
signal in time series photometry.
For the primary \kepler\ mission, the noise induced by instrumental artifacts
on transit timescales was significantly smaller than transit depths for
all but the smallest planets.
With \KT\ this is no longer the case.
The motion of the instrument causes a drift in the pointing of approximately
$1''$ per hour, causing variations in the flat field to dominate the
photometric signal.

As a result, artifacts in the data induced by pointing jitter can ...

If the properties of the noise in the data can be fully understood and
modeled, such artifacts can be separated from true astrophysical events.
Our model, however, makes no assumptions about the properties of the noise
other than that it is correlated across many stars on the detector.
Therefore, our model can occassionally be fooled by instrumental artifacts
that a more sophisticated method, or the human eye, can easily separate
from true astrophysical signals.

To this end, we (euphamism for look at by eye) each system to identify the
most promising, likely astrophysical signals.

>>>>

\dfmtodo{Iterative search.}

\paragraph{Initial candidate list}

To generate an initial candidate list, we estimate the signal-to-noise of
each candidate in the \TIC\ periodogram by comparing the peak height to a
robust estimate of variance in \TIC\ values across period.
A cut in this quantity can reject most variable stars and low
signal-to-noise candidates that can't be reliably recovered from the data.
Figure SOMEFIGURE shows the distribution of signal-to-noise for a set of
injections and compares it to the distribution of false candidates that are
proposed by the pipeline.
To minimize contamination from false alarms but maximize our sensitivity, we
choose a threshold of 15 \dfmtodo{right number?}.
We also find that the signals with periods $\lesssim 4$ days are very
contaminated by false alarms.
This might be due to the fact that our independence assumption (SOMEEQUATION)
breaks down at these short periods.
Therefore, we discard all signals with periods shorter than 4 days.
After these cuts, we're left with 700 \dfmtodo{right number?} candidates that
we then examine by hand.
The full list of peaks and their relevant meta data is available online at
\dfmtodo{SOMEURL}.

@@

After our initial cuts on the candidate list, the majority of signals are
still false alarms mostly due to variable stars or single outlying data
points.
It should be possible to construct a more robust machine vetting algorithm
that discards these samples without missing real transits (CITE SOME THINGS)
but for the purposes of this \paper, we simply inspect the light curve for
each of the YYYY candidates \emph{by hand} to discard signals that are not
convincing transits.
The results of this vetting can be seen online at SOMEURL.

This vetting resulted in a list of ZZZZ transiting candidates.
Many of these signals are due to astrophysical ``false positives'' like
eclipsing binaries or blending.
We address this effect in the following section and separate the list of
candidates into a list of astrophysical false positives and planet candidates.
